Software Ticket Quality

### 2017-10-16 proposal/mprop.tex
Added 8th paper

\textbf{Recognizing Contextual Polarity}\cite{wilson2005recognizing}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The paper's main goal is to find efficient ways to distinguish between 
    contextual and prior polarity.
  \item \textbf{What was the method?}
    They used a two step method that used machine learning and a variety of
    features. The first step classified each phrase which had a clue as either
    neutral or polar, followed by taking all phrases marked in the previous step
    and giving them a contextual polarity (e.g.\ positive, negative, both, neutral).
  \item \textbf{What did they learn?}
    Through the method the authors employed, they managed to automatically identify
    the contextual polarity. As most papers were only looking at the sentiment  
    extracted from the overall document, they managed to get valuable results
    from looking at specific words and phrases.
  \item \textbf{Relevance to our work}: when analyzing the description and
    comments of the ticket, we can use their method for accurately 
    infering the sentiment transmitted.
\end{itemize}

>>>>

\textbf{Thumbs Up or Thumbs Down}\cite{turney2002thumbs}:
\begin{itemize}
  \item \textbf{What were the goals?}
  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}

\textbf{Thumbs Up or Thumbs Down}\cite{turney2002thumbs}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to detect the overall sentiment transmitted
    through reviews of various types.
  \item \textbf{What was the method?}
    The author created an unsupervised machine learning algorithm that was 
    evaluated on more than 400 reviews on Epinions on various kinds of markets 
    (e.g.\ automobiles, movie). The algorithm implementation was divided 
    into three steps:
      \begin{itemize}
        \item extract phrases containing adjectives or adverbs;
        \item estimate the semantic orientation of the phrases;
        \item classify the review as recommended or not recommended based on
          the semantic orientation calculated at previous step.
      \end{itemize}
  \item \textbf{What did they learn?}
    One thing the author learned that different categories will yield different 
    results. For example, the automobile section on Epinions ranked much higher, 
    84\%, compared to movie reviews, which had an accuracy of 65.83\%. Moreover, 
    most pitfalls of the algorithm could be attributed to multiple factors, such 
    as not using a supervised learning system or limitations of PMI-IR.
  \item \textbf{Relevance to our work}: the method can be applied for extracting
    sentiments from the tickets (description and comments) we will use 
    in our own research.
\end{itemize}

\textbf{Recognizing Contextual Polarity}\cite{wilson2005recognizing}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The paper's main goal is to find efficient ways to distinguish between 
    contextual and prior polarity.
  \item \textbf{What was the method?}
    They used a two step method that used machine learning and a variety of
    features. The first step classified each phrase which had a clue as either
    neutral or polar, followed by taking all phrases marked in the previous step
    and giving them a contextual polarity (e.g.\ positive, negative, 
    both, neutral).
  \item \textbf{What did they learn?}
    Through the method the authors employed, they managed to automatically 
    identify the contextual polarity. As most papers were only looking at the 
    sentiment extracted from the overall document, they managed to get valuable 
    results from looking at specific words and phrases.
  \item \textbf{Relevance to our work}: when analyzing the description and
    comments of the ticket, we can use their method for infering the sentiment 
    transmitted probably more accurately than the technique used in 
    Turney's paper\cite{turney2002thumbs}.
\end{itemize}
